Template for manuscript

### 2024-12-10 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.tex
Work on manuscript

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Thu Dec  5 16:44:34 2024
\begin{table}[ht]
\centering
\caption{Lakes included in the experiment, along with treatment
                and general characteristics.} 
\label{tab:lakes}
\begin{tabular}{lllllll}
  \toprule
Lake & Treatment & Latitude (°N) & Longitude (°E) & Altitude (m) & Area (hectare) & Maximum Depth (m) \\ 
  \midrule
B1P1 & Fish & 61.15338 & -45.57081 & 272 & 0.21 & 4.00 \\ 
  B2P2 & Fish & 61.12299 & -45.55988 & 255 & 0.50 & 3.00 \\ 
  B3P3 & Fish & 61.13385 & -45.57556 & 258 & 0.30 & 5.00 \\ 
  B2P3 & Fish & 61.12275 & -45.55696 & 261 & 0.41 & 4.25 \\ 
  B3P1 & Fish & 61.13130 & -45.51195 & 180 & 0.40 & 2.00 \\ 
  B3P2 & Fish & 61.12788 & -45.51031 & 201 & 0.53 & 4.50 \\ 
  B1P4 & No Fish & 61.16552 & -45.56801 & 304 & 0.44 & 2.20 \\ 
  B2P4 & No Fish & 61.12192 & -45.55497 & 261 & 0.51 & 7.00 \\ 
  B3P0 & No Fish & 61.13210 & -45.51416 & 177 & 0.81 & 4.00 \\ 
  ERL85 & No Fish & 61.14171 & -45.59328 & 120 & 1.82 & 8.00 \\ 
  ERL122 & No Fish & 61.14182 & -45.53623 & 111 & 1.10 & 5.00 \\ 
  ERL152 & No Fish & 61.14646 & -45.59235 & 156 & 0.73 & 4.50 \\ 
   \bottomrule
\end{tabular}
\end{table}

@@

\begin{gather}
x^{2} \label{eq:sys1}\\
x^{3} \label{eq:sys2}
\end{gather}

>>>>

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Tue Dec 10 16:08:53 2024
\begin{table}[ht]
\centering
\caption{Lakes included in the experiment, along with treatment
                and general characteristics.} 
\label{tab:lakes}
\begin{tabular}{lllllll}
  \toprule
Lake & Treatment & Latitude (°N) & Longitude (°E) & Altitude (m) & Area (hectare) & Maximum Depth (m) \\ 
  \midrule
B1P1 & Fish & 61.15338 & -45.57081 & 272 & 0.21 & 4.00 \\ 
  B2P2 & Fish & 61.12299 & -45.55988 & 255 & 0.50 & 3.00 \\ 
  B3P3 & Fish & 61.13385 & -45.57556 & 258 & 0.30 & 5.00 \\ 
  B2P3 & Fish & 61.12275 & -45.55696 & 261 & 0.41 & 4.25 \\ 
  B3P1 & Fish & 61.13130 & -45.51195 & 180 & 0.40 & 2.00 \\ 
  B3P2 & Fish & 61.12788 & -45.51031 & 201 & 0.53 & 4.50 \\ 
  B1P4 & No Fish & 61.16552 & -45.56801 & 304 & 0.44 & 2.20 \\ 
  B2P4 & No Fish & 61.12192 & -45.55497 & 261 & 0.51 & 7.00 \\ 
  B3P0 & No Fish & 61.13210 & -45.51416 & 177 & 0.81 & 4.00 \\ 
  ERL85 & No Fish & 61.14171 & -45.59328 & 120 & 1.82 & 8.00 \\ 
  ERL122 & No Fish & 61.14182 & -45.53623 & 111 & 1.10 & 5.00 \\ 
  ERL152 & No Fish & 61.14646 & -45.59235 & 156 & 0.73 & 4.50 \\ 
   \bottomrule
\end{tabular}
\end{table}

@@

\begin{gather}
\alpha^{\ast}_{t} =
\begin{cases}
\alpha_{t-1} + \alpha_{t}, & \text{if } k_{t} = 0, \\
\frac{\alpha_{t}}{k_{t-1}} + \frac{-\exp{(-k_{t-1})}\alpha_{t}}{k_{t-1}} +
\exp{(-k_{t-1})}\alpha_{t-1}, & \text{otherwise},
\end{cases} \label{eq:sys1} \\
\alpha_{t} = \mathbf{X}_{t-1}\bm{\beta} + k_{t-1}O_{s,t-1}, \label{eq:sys2} \\
k_{t} = \frac{K^{\ast}_{t}\Delta t}{z_{t}}. \label{eq:sys3}
\end{gather}

In this equation structure, $k_{t}$ is the coefficient of gas exchange;
$\mathbf{X}$ is an $n \times 2$ matrix of predictor variables with $I$
(irradiation in arbitrary light units) in the first column and $\ln{T}$ (\textdegree{}$C$) in the second
column; $\bm{\beta}$ is a $2 \times 1$ vector of parameters to be estimated
($\iota$, $\rho$). $\iota$ represents the parameter for Gross Primary Production
(hereafter GPP), implying a linear relationship between GPP and irradiation, and $\rho$ represents
the parameter for Respiration (hereafter R), implying a log-linear relationship
between R and temperature; $O_{s}$ is the equilibrium DO concentration at
supplied conditions; $K^{\ast}_{t}$ is a stochastic node,
with $K^{\ast}_{t} \sim N(K_{t}, \sigma_{k})$, where $K_{t}$ is the gas exchange
coefficient, and $\sigma_{k}$ the precision thereof; the default precision
is $1/(0.1 \times K_{t})$; finally, $z_{t}$ is the mixed layer depth.

From equation~\ref{eq:sys1}, we can see that if $k_{t} = 0$ (i.e., no gas exchange
with the atmosphere), the oxygen levels in the water are modeled to be additive for each
time step. Furthermore, we can see that the gas exchange coefficient is dependent
on mixed layer depth (equation~\ref{eq:sys3}).

While the estimate of gas exchange coefficient serves as prior information for $K$,
priors for the fitted GPP and R parameters ($\iota$ and $\rho$) can also
be defined. The default priors for $\iota$ and $\rho$ are normal distributions
with mean 0 and variance $1 \times 10^{5}$
($\iota_{t} \sim N(0,10^{5})$, $\rho_{t} \sim N(0,10^{5})$) and were used in our case.

To estimate metabolism, the median of the posterior distribution of the parameters
is used as a scalar estimate. Daily GPP and R estimates represent an integrated
estimate of these scalars over a 24-hour window. Uncertainty of GPP and R
estimates is expressed as the posterior standard deviation of the respective
parameters ($\iota$ and $\rho$), multiplied by the square root of the corresponding
covariate ($I$ and $\ln{T}$). NEP is the sum of GPP and R, and the standard deviation
of NEP is the sum of the standard deviations for GPP and R.

In total, 5 parameters are fit in this Bayesian model, namely $\iota$, $\rho$,
$K$, $\tau_{v}$, and $\tau_{w}$. For all parameters except $K$, (default) minimally
informative priors were used. Regarding $K$, as described above, its estimate
(from the separate gas transfer coefficient model) serves as a prior.

Estimates of the posterior distribution of the parameters were sampled using
Gibbs sampling implemented in Just Another Gibbs Sampler
(\href{https://sourceforge.net/projects/mcmc-jags/files/}{JAGS}). Prior to running
the Bayesian model, it must be installed.

\subsection{Sensitivity analysis for mixed layer depth} \label{subsec:sens}

As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
data to estimate mixed layer depth. An initial approach to deal with that problem
was to investigate the effect of different mixed layer depths on the daily metabolism
estimates. For that purpose, we selected a few lakes for different monitoring
periods (2021, 2022, 2023) and assessed the impact of various, constant
mixed layer depths over time on the metabolism results.

\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Lade nötiges Paket: grid}}\end{kframe}datetime  dsr_cor      wsp     Pond   do.obs      wtr 
       0        0        0        0      154        0 
[1] 0

{\centering \includegraphics[width=\maxwidth]{plots/psensanal-1}

}

[1] 0
[1] "Points removed due to incomplete day or duplicated time step: 0"
[1] "NA's added to fill in time series: 0"
[1] "using allK model"
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# module glm loaded}}\end{kframe}Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16998

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16988

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16925

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17003

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17076

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16921

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16947

Initializing model

[1] "Points removed due to incomplete day or duplicated time step: 0"
[1] "NA's added to fill in time series: 0"
[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16998

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16988

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16925

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17003

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17076

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16921

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16947

Initializing model

[1] "Points removed due to incomplete day or duplicated time step: 0"
[1] "NA's added to fill in time series: 0"
[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16998

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16988

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16925

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17003

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17076

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16921

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16947

Initializing model

[1] "Points removed due to incomplete day or duplicated time step: 0"
[1] "NA's added to fill in time series: 0"
[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16998

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16988

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16925

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17003

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17076

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16921

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16947

Initializing model

[1] "Points removed due to incomplete day or duplicated time step: 0"
[1] "NA's added to fill in time series: 0"
[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16998

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16988

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16925

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17003

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17076

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16921

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16947

Initializing model

[1] "Points removed due to incomplete day or duplicated time step: 0"
[1] "NA's added to fill in time series: 0"
[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16998

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16988

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16925

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17003

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17076

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16921

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16947

Initializing model

[1] "Points removed due to incomplete day or duplicated time step: 0"
[1] "NA's added to fill in time series: 0"
[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16998

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16988

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16925

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17003

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17076

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16921

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16947

Initializing model

[1] "Points removed due to incomplete day or duplicated time step: 0"
[1] "NA's added to fill in time series: 0"
[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16998

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16988

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16925

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17003

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 17076

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16921

Initializing model

[1] "using allK model"
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
Graph information:
   Observed stochastic nodes: 719
   Unobserved stochastic nodes: 1442
   Total graph size: 16947

Initializing model

$y
expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, 
    ")"))

attr(,"class")
[1] "labels"
$y
expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", 
    NULL^-1, ")"))

attr(,"class")
[1] "labels"
\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}\end{kframe}

{\centering \includegraphics[width=\maxwidth]{plots/psensanal-2}

}
